---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spacetimeview

<!-- badges: start -->

<!-- badges: end -->

spacetimeview generates an interactive space time data dashboard in one
line of code. You provide the data with columns of GPS coordinates (or
sf geometries) and a column of times and spacetimeview will turn it into
an interactive plot.

You can use the plot as a static website html file to share with others
(hostable for free on services like github pages) or as an interactive
html widget to explore your data.

## Installation

You can install the development version of spacetimeview from
[GitHub](https://github.com/) with:

```{r install}
# after cloning with `git clone git@github.com:jakemanger/spacetimeview.git`
devtools::load_all()
# or install from github
# install.packages("devtools")
# devtools::install_github("jakemanger/spacetimeview")
```

## Example

Load your data with GPS coordinates and datetimes:

```{r load_data}
library(spacetimeview)
d <- read.csv('https://raw.githubusercontent.com/uber-web/kepler.gl-data/master/earthquakes/data.csv')
d <- d[,c('Latitude', 'Longitude', 'DateTime', 'Magnitude')]
```

Now, in one line of code, generate an interactive plot over space and
time

```{r make_plot}
spacetimeview(d)
```

Note, this interactive plot is also a website, that you can save as a
html file

```{r save_plot_as_html, echo = FALSE}
htmlwidgets::saveWidget(spacetimeview(d), "my_plot.html")
```

and simply deploy to any website host, even free static site hosts like
Github Pages

```{r deploy_to_gh_pages}
# automate GitHub Pages setup to deploy html files in the `docs` folder
usethis::use_github_pages(branch='main', path='/docs')

# move the my_plot.html we just generated to the docs folder and push it to github
system("mkdir -p docs/")
system("mv ./my_plot.html ./docs/index.html")
system("git add docs/index.html")
system("git commit -m 'Deploy spacetimeview widget to GitHub Pages'")
system("git push")
```

Now if you navigate to the link provided above (e.g.
<https://jakemanger.github.io/spacetimeview/>) you should see your data
displayed in a responsive and interactive space time view.
